### 2019-10-10 tim-lucas-model-ensembles.tex
Add experimental condition names and Malagasy acknowledgement.

We compared the performance of the models with five sets of covariates, $X$.
Firstly, we used the environmental and anthropogenic covariates, centered and standardised as a baseline model.
Secondly, we used the predictions from the machine learning models trained on local data.
Thirdly, we combined the predictions from the machine learning models and the environmental coviarates in one model.
Fourthly, we used predictions from the machine learning models trained on the global data.
Finally, we combined predictions from the machine learning models trained on regional data and global data.

@@

>>>>

We compared the performance of the models with five sets of covariates, $X$.
Firstly, we used the environmental and anthropogenic covariates, centered and standardised as a baseline model (subsequantly called Enviro).
Secondly, we used the predictions from the machine learning models trained on local data (ML\textsubscript{l}).
Thirdly, we combined the predictions from the machine learning models and the environmental coviarates in one model (Enviro + ML\textsubscript{l}).
Fourthly, we used predictions from the machine learning models trained on the global data (ML\textsubscript{g}).
Finally, we combined predictions from the machine learning models trained on regional data and global data (ML\textsubscript{l} + ML\textsubscript{g}).

@@

\section*{Acknowledgments}
The authors acknowledge the National Malaria Control Programme of Madagascar for sharing their routine case data for this analysis.
